[Result, but poetic]: Does LLM Use Improve Data Science Education?

### 2024-07-18 paper/paper.qmd
cleaned some more, made a visualization

@@

>>>>

```{r}
# Import data (CHANGE WHEN FULLY CLEAN!)
raw_data <- read_csv("data/raw_data/raw_STA302_postcourse_survey_w24.csv")
```

@@

```{r}
#Histogram of GPA

raw_data |>
  ggplot(aes(x = gpa)) +
  geom_histogram(binwidth = 0.1, fill = "skyblue", color = "black") +
  labs(title = "Distribution of GPAs in the Survey Data",
       x = "GPA",
       y = "Frequency") +
  theme_minimal()

```
